### 2019-04-03 Model.tex
Updates from Overleaf

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure \cite{rumelhart1988learning} (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
  We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$.   
  % \kechen{It's still possible for the model to predict a label twice. I'd like to see a mathematical treatment of this case in your framework. Would you treat the predicted multiset as a set by ignoring repeated entries? Would you force the probability of a multiset down to zero? The mere fact that these can be predicted by the model means that they should eat away at some of the probability mass devoted to pure sets. You need a way of handling this. }
  To be precise, our label ``permutations'' $\pi$ are sequences that allow repetitions (i.e.\ $(y_1,y_2,y_3,y_1,...)$), up to a maximum length. So the set probability sums over all such permutations, and both training and prediction candidate sets are generated this way. In practice, we do not think this detail makes any difference, as sequences with repeated labels are extremely rare; however in theory we want to allow the attention context to focus on any recent labels it chooses to (repeated if necessary).

@@

This training objective (\ref{eq:right_obj}) looks similar to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired  consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. 
Using Jensen’s inequality, one can show that the total probability mass in Eq. 3 will be less than or equal to the true amount of probability mass in Eq. 1. In this sense, previous work is optimizing a bound on the log-likelihood, while we are optimizing it directly.

If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability will still be low in Eq. 3. In other words, if for each document, RNN finds one  good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model will be penalized heavily.  As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the  summation operation, it suffices to find only one reasonable permutation of the labels for each document. \emph{Different documents can have different label orders}; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than  (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, does not suffer from self reinforcement issue and can serve as a stand alone training objective. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

    % \underline{function Beam\_Search\_for\_Given\_Set} $(\mathbf{y},m)$\;
    \Input{Instance $x$ \\
    Subset of labels considered $G\subset \mathcal{L}$\\
    Boolean flag $ALL$: 1 if sequences must contain all $G$ labels; 0 if partial sequences are allowed }
    \Output{A list of top sequences and the associated probabilities} 
    Let $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$ be the top $K$ sequences  found so far. Initially, all $K$ sequences are empty. $\oplus$ means concatenation. \\
    % Let $C$ be the set of candidate sequences, initially empty.\\
    \While {true}{
     // Step 1: Generate Candidate Sequences from each existing sequence $s_k \in K$ and all possible new labels $l \in G\setminus s_k$:\\
    Expand all non-stopped sequences:\\
     % $C = \{ \mathbf{s}_k\oplus l | l\in G,  l \notin s_k, STOP \notin s_k \}$\\
     $C = \{ \mathbf{s}_k\oplus l | l\in G, STOP \notin s_k \}$\\    
Include stopped sequences:\\
    $C = C \cup \{ \mathbf{s}_k | STOP \in s_k \}$\\
    Terminate non-stopped sequences:\\
    \If{$ALL==0$}{
    % Add $\mathbf{s}_k\oplus STOP$ to $C$  }
    %
    $C =C \cup \{ \mathbf{s}_k\oplus STOP | STOP \notin s_k \}$
    }

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up sequence (permutation) probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set. Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ high probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine}). This approximate inference procedure is carried out repeatedly before each batch training step, in order to find high probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

@@

    % Initialize model parameters\\
    \ForEach {batch}{
        % \ForEach {batch }{
            \ForEach{$(x^{n},\mathbf{y}^{n})$ in the batch}{
                Get top $K$ sequences :\\
		    	$\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}, p(\mathbf{s}^n_{1}|x^n),...,p(\mathbf{s}^n_{K}|x^n)\}$=  \hspace{4ex}=Beam\_Search($(x^{n},\mathbf{y}^{n}, ALL=1$)\\
                }
            Update model parameters by maximizing $\sum\limits_{(x^{n},\mathbf{y}^{n}) \in \text{batch}} \log \sum\limits_{\mathbf{s}\in\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}\}} p(\mathbf{s}|x^{n})$
        % }
    }
    \caption{Training method for set-RNN}
    \label{alg:train_beam}
\end{algorithm}

\subsection{Predicting the Most Probable Set}
The transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$ also naturally leads to a prediction procedure, which is different from the previous standard of directly using most probable sequence as a set. We instead aim to find the most likely set $\hat{\mathbf{y}}=\arg\max_{\mathbf{y}} p(\mathbf{y}|x)$, which involves summing up probabilities for all of its permutations (see Table~1). To make it tractable, we propose a two-level beam search procedure. First we run standard RNN beam search (Algorithm \ref{alg:beam_combine}) to generate a list of high probability sequences.  We then consider the label set associated with each label sequence.  For each set, we evaluate its probability using the same approximate summation procedure as the one used during model training (Algorithm~\ref{alg:beam_combine}): we run our modified beam search to find the top few high probability sequences associated with the set and sum up their probabilities. Among these sets that we have evaluated, we choose the one with the highest probability as the prediction. The overall prediction procedure is summarized in Algorithm~\ref{alg:test}. As we shall show in case study, the most probable set may not correspond to the most probable sequence; these are certainly cases where our method has an advantage.
%\textbf{Variant of beam search.} To obtain the top high probability sequences associated with a given set, beam search

Both our method and the comparison sate-of-the-art (Vinyals-RNN) take more time than a vanilla-RNN, by a factor of $K$, because there are $K$ permutations considered for each datapoint. Our proposed method is about as fast as the Vinyals-RNN methods, except for the Vinyals-RNN-uniform which is a bit faster (by a factor of 1.5) because its epochs do not run the additional forward pass.

@@

 %   \underline{function Euclid} $(a,b)$\;
    \Input{Instance $x$}
    \Output{Predicted label set $\hat{\mathbf{y}}$}
    Obtain $K$ highest probability sequences :\\
    $\{\mathbf{s}_1,...,\mathbf{s}_{K}\}$ =  Beam\_Search((x,$\mathcal{L}, ALL=0$)\\

@@

         Get $K$ most probable sequences associated with $\mathbf{y}_k$ and their probabilities :\\
	   $\{\mathbf{s'}_{1},...,\mathbf{s'}_{K}, p(\mathbf{s}'_{1}|x),...,p(\mathbf{s}'_{K}|x)\}$= \\ \hspace{6ex} =Beam\_Search((x,$\mathbf{y}_k, ALL=1$)\\
       Set probability is approx by summing up :
        $p({\mathbf{y}_k}|x) \approx \sum\limits_{\mathbf{s}\in \{\mathbf{s}'_{1},...,\mathbf{s}'_K\}} p(\mathbf{s}|x)$
    }    
    $\hat{\mathbf{y}} = argmax_{{\mathbf{y}_k}}(p({\mathbf{y}_k}|x))$
    \caption{Prediction Method for Set-RNN}
    \label{alg:test}
\end{algorithm}

>>>>

We propose a new way of adapting RNN to multi-label set prediction, which we call \emph{set-RNN}. We appreciate the RNN model structure \cite{rumelhart1988learning} (defines a probability distribution over all possible sequences directly) and introduce training and prediction objectives tailored for sets that take advantage of it, while making a clear distinction between the sequence probability $p(\mathbf{s}|x)$ and the set probability $p(\mathbf{y}|x)$. 
% We notice that previous work either lack an explicit definition of set probability, or use sequence probability as the set probability, or transform sequence probability into set probability in an ad hoc way. 
% We notice that while the idea of using RNN for multi-label prediction has a lot of advantages and potentials, the existing adaptations of RNN to set prediction task are not well justified and have several issues.
 % In the literature, these two are often used interchangeably.
 % A standard RNN model only defines a probability distribution over all possible sequences directly, as mentioned earlier.
 We define the set probability as the sum of sequences probabilities for all sequence permutations of the set, namely $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. Based on this formulation, an RNN also defines a probability distribution over all possible sets indirectly since $\sum_{\mathbf{y}} p(\mathbf{y}|x)=\sum_{\mathbf{y}}\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)=\sum_{\mathbf{s}} p(\mathbf{s}|x)=1$.  (For this equation to hold, in theory, we should also consider permutations $\mathbf{s}$ with repeated labels, such as $(1,2,3,1)$. But in practice, we find it very rare for RNN to actually generate sequences with repeated labels in our setup, and whether allowing repetition or not does not make much difference.)
 % \kechen{It's still possible for the model to predict a label twice. I'd like to see a mathematical treatment of this case in your framework. Would you treat the predicted multiset as a set by ignoring repeated entries? Would you force the probability of a multiset down to zero? The mere fact that these can be predicted by the model means that they should eat away at some of the probability mass devoted to pure sets. You need a way of handling this. }
%  To be precise, our label ``permutations'' $s$ are sequences that allow repetitions (i.e.\ $(1,2,3,1,...)$), up to a maximum length. In order to define a valid distribution, we must allow sequences to have repetitions in theory, but in practice %So the set probability sums over all such permutations, and both training and prediction candidate sets are generated this way. In practice, 
%  we do not think this detail makes any difference, as sequences with repeated labels are extremely rare; however in theory we want to allow the attention context to focus on any recent labels it chooses to (repeated if necessary).

@@

This training objective (\ref{eq:right_obj}) looks similar to the objective (\ref{eq:wrong_obj}) considered in previous work \cite{vinyals2015order}, but in fact they correspond to very different transformations. Under the maximum likelihood framework, our objective (\ref{eq:right_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$, while objective (\ref{eq:wrong_obj}) corresponds to the transformation $p(\mathbf{y}|x)=\prod_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$. The latter transformation does not define a valid probability distribution over $\mathbf{y}$ (i.e., $\sum_{\mathbf{y}} p(\mathbf{y}|x)\neq 1$), and it has an undesired consequence in practical model training: because of the multiplication operation, the RNN model has to assign equally high probabilities to all sequence permutations of the given label set in order to maximize the set probability. If only some sequence permutations receive high probabilities while others receive low probabilities, the set probability computed as the product of sequence probabilities will still be low. In other words, if for each document, RNN finds one good way of ordering relevant labels (such as hierarchically) and allocates most of the probability mass to the sequence in that order, the model still assigns low probabilities to the ground truth label sets and will be penalized heavily. As a consequence the model has little freedom in discovering and concentrating on some natural label order. In contrast, with our proposed training objective, in which the multiplication operation is replaced by the summation operation, it suffices to find only one reasonable permutation of the labels for each document. It is worth noting that different documents can have different label orders; thus our proposed training objective gives the RNN model far more freedom on label order. The other two objectives (\ref{eq:max_obj}) and (\ref{eq:sample_obj}) proposed in \cite{vinyals2015order} are less restrictive than (\ref{eq:wrong_obj}), but they have to work in conjunction with (\ref{eq:wrong_obj}) because of the self reinforcement issue. Our proposed training objective has a natural probabilistic interpretation, and does not suffer from self reinforcement issue. Thus it can serve as a stand alone training objective. Also, using Jensen’s inequality, one can show that objective (\ref{eq:wrong_obj}) is maximizing a lower bound on the log-likelihood, while objective (\ref{eq:right_obj}) is maximizing it directly. 
% Another approach used in previous work, which is to pick one fixed sequence order (e.g., by label frequency) in advance, forces the model to only assign high probabilities to sequences in that order.
% , and therefore does not leave any opportunity for the model to explore label orders. Since in multi-label data, labels often do not have an obvious ordering and human heuristics are often suboptimal, it is advantageous to let the training procedure discover label orderings, on a per sample basis.
% \subsection{A Brief Review of RNN and Attention}

\begin{algorithm}[ht]
  \SetKwInOut{Input}{Input}
  \SetKwInOut{Output}{Output}

  % \underline{function Beam\_Search\_for\_Given\_Set} $(\mathbf{y},m)$\;
  \Input{Instance $x$ \\
  Subset of labels considered $G\subset \mathcal{L}$\\
  Boolean flag $ALL$: 1 if sequences must contain all $G$ labels; 0 if partial sequences are allowed }
  \Output{A list of top sequences and the associated probabilities} 
  Let $\mathbf{s}_1$,$\mathbf{s}_2$,...,$\mathbf{s}_K$ be the top $K$ sequences found so far. Initially, all $K$ sequences are empty. $\oplus$ means concatenation. \\
  % Let $C$ be the set of candidate sequences, initially empty.\\
  \While {true}{
   // Step 1: Generate Candidate Sequences from each existing sequence $s_k \in K$ and all possible new labels $l \in G$:\\
  Expand all non-stopped sequences:\\
   % $C = \{ \mathbf{s}_k\oplus l | l\in G, l \notin s_k, STOP \notin s_k \}$\\
   $C = \{ \mathbf{s}_k\oplus l | l\in G, STOP \notin s_k \}$\\  
Include stopped sequences:\\
  $C = C \cup \{ \mathbf{s}_k | STOP \in s_k \}$\\
  Terminate non-stopped sequences:\\
  \If{$ALL==0$}{
  % Add $\mathbf{s}_k\oplus STOP$ to $C$ }
  %
  $C =C \cup \{ \mathbf{s}_k\oplus STOP | STOP \notin s_k \}$
  }

@@

\subsection{Training by Maximizing Set Probability}
Training an RNN model with the proposed objective (\ref{eq:right_obj}) requires summing up sequence (permutation) probabilities for a set $\mathbf{y}$, where $|\mathbf{y}|$ is the cardinality of the set. Thus evaluating this objective exactly can be intractable. We can approximate this sum by only considering the top $K$ highest probability sequences produced by the RNN model. We introduce a variant of beam search for sets with width $K$ and with the search candidates in each step restricted to only labels in the set (see Algorithm~\ref{alg:beam_combine} with $ALL=1$)%\footnote{The ``ALL'' flag determines if the sequences can terminate with a partial subset of labels (as used in Algorithm~\ref{alg:test} line 2) or a full set is required (as used in Algorithm~\ref{alg:train_beam} line 4 and Algorithm~\ref{alg:test} line 7).}
. This approximate inference procedure is carried out repeatedly before each batch training step, in order to find highest probability sequences for all training instances occurring in that batch. The overall training procedure is summarized in Algorithm \ref{alg:train_beam}.% \cheng{add pseudo code}

@@

  % Initialize model parameters\\
  \ForEach {batch}{
    % \ForEach {batch }{
      \ForEach{$(x^{n},\mathbf{y}^{n})$ in the batch}{
        Get top $K$ sequences :\\
		  	$\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}, p(\mathbf{s}^n_{1}|x^n),...,p(\mathbf{s}^n_{K}|x^n)\}$= \hspace{4ex}= Beam\_Search$(x^{n},\mathbf{y}^{n}, ALL=1$)\\
        }
      Update model parameters by maximizing $\sum\limits_{(x^{n},\mathbf{y}^{n}) \in \text{batch}} \log \sum\limits_{\mathbf{s}\in\{\mathbf{s}^n_{1},...,\mathbf{s}^n_{K}\}} p(\mathbf{s}|x^{n})$
    % }
  }
  \caption{Training method for set-RNN}
  \label{alg:train_beam}
\end{algorithm}

\subsection{Predicting the Most Probable Set}
The transformation $p(\mathbf{y}|x)=\sum_{\mathbf{s}\in \pi(\mathbf{y})} p(\mathbf{s}|x)$ also naturally leads to a prediction procedure, which is different from the previous standard of directly using most probable sequence as a set. We instead aim to find the most likely set $\hat{\mathbf{y}}=\arg\max_{\mathbf{y}} p(\mathbf{y}|x)$, which involves summing up probabilities for all of its permutations. To make it tractable, we propose a two-level beam search procedure. First we run standard RNN beam search (Algorithm \ref{alg:beam_combine} with $ALL=0$) to generate a list of highest probability sequences. We then consider the label set associated with each label sequence. For each set, we evaluate its probability using the same approximate summation procedure as the one used during model training (Algorithm~\ref{alg:beam_combine} with $ALL=1$): we run our modified beam search to find the top few highest probability sequences associated with the set and sum up their probabilities. Among these sets that we have evaluated, we choose the one with the highest probability as the prediction. The overall prediction procedure is summarized in Algorithm~\ref{alg:test}. As we shall show in case study, the most probable set may not correspond to the most probable sequence; these are certainly cases where our method has an advantage.
%\textbf{Variant of beam search.} To obtain the top high probability sequences associated with a given set, beam search

Both our method and the competitor state-of-the-art (Vinyals-RNNs) are at most $K$ times slower than a vanilla-RNN,  due to the time spent on dealing with $K$ permutations per datapoint. Our proposed method is about as fast as the Vinyals-RNN methods, except for the Vinyals-RNN-uniform which is a bit faster (by a factor of 1.5) because its epochs do not run the additional forward pass.

@@

 %  \underline{function Euclid} $(a,b)$\;
  \Input{Instance $x$}
  \Output{Predicted label set $\hat{\mathbf{y}}$}
  Obtain $K$ highest probability sequences :\\
  $\{\mathbf{s}_1,...,\mathbf{s}_{K}\}$ =  Beam\_Search(x,$\mathcal{L}, ALL=0$)\\

@@

     Get $K$ most probable sequences associated with $\mathbf{y}_k$ and their probabilities :\\
	  $\{\mathbf{s'}_{1},...,\mathbf{s'}_{K}, p(\mathbf{s}'_{1}|x),...,p(\mathbf{s}'_{K}|x)\}$= \\ \hspace{6ex} = Beam\_Search(x,$\mathbf{y}_k, ALL=1$)\\
    Set probability is approx by summing up :
    $p({\mathbf{y}_k}|x) \approx \sum\limits_{\mathbf{s}\in \{\mathbf{s}'_{1},...,\mathbf{s}'_K\}} p(\mathbf{s}|x)$
  }  
  $\hat{\mathbf{y}} = argmax_{{\mathbf{y}_k}}(p({\mathbf{y}_k}|x))$
  \caption{Prediction Method for set-RNN}
  \label{alg:test}
\end{algorithm}

### 2019-04-03 results.tex
Updates from Overleaf

We test our proposed set-RNN method on 4 real-world datasets, RCV1-v2, Slashdot, TheGuardian, and Arxiv Academic Paper Dataset (AAPD) \cite{DBLP:journals/corr/abs-1806-04822}. We take the public RCV1-v2 release\footnote{\scriptsize\url{http://www.ai.mit.edu/projects/jmlr/papers/volume5/lewis04a/lyrl2004_rcv1v2_README.htm}} and randomly sample 50,000 documents. We crawl Slashdot and TheGuardian documents from their websites\footnote{\scriptsize Slashdot: \url{https://slashdot.org/} Note that there is another public Slashdot multi-label dataset \cite{read2009classifier} but we do not use that one because it is quite small. TheGuardian: \url{https://www.theguardian.com}  
} and treat the official editor tags as ground truth. We also gather a list of user tags\footnote{\scriptsize \url{www.zubiaga.org/datasets/socialbm0311/}} for each document and treat them as additional features. For AAPD dataset, we follow the same train/test split as in \cite{DBLP:journals/corr/abs-1806-04822}. Table \ref{tab:stats} contains statistics of these four datasets. 
\begin{table}[h]
	\resizebox{1.01\columnwidth}{!}{%resize the table
\begin{tabular}{|l|c|c|c|c|c|c|}
  \hline
  Data & \#Train & \#Test & Cardinality & \#Labels & Doc length  \\
  \hline
  Slashdot & 19,258 & 4,814& 4.15& 291&64 \\
  RCV1-v2 & 40,000& 10,000&  3.17& 101&121 \\
  TheGuardian & 37,638 & 9,409 & 7.41& 1,527&505 \\
  AAPD & 53,840 & 1,000 & 2.41& 54 & 163 \\
  \hline
\end{tabular}
}
\caption{\fontsize{10}{12}\selectfont  Statistics of the datasets.}\label{tab:stats}
\end{table}

\begin{table*}[ht]
	\begin{center}
	\resizebox{2.1\columnwidth}{!}{%resize the table
		\begin{tabular}{|l|cc|cc|cc|cccc|}
			\hline
			\multirow{2}{*}{Methods}	&  
             \multicolumn{2}{c|}{Slashdot}&\multicolumn{2}{c|}{RCV1-v2}&\multicolumn{2}{c|}{TheGuardian}&\multicolumn{4}{c|}{AAPD} \\
             \cline{2-11}
           & label-F1 & instance-F1  & label-F1 & instance-F1 & label-F1 & instance-F1 & label-F1 & instance-F1 & Hamming-Loss & Micro-F1 \\

@@

 To process documents, we filter out stopwords and punctuations. Each document is truncated to have maximum 500 words for TheGuardian and AAPD, and 120 for Slashdot and RCV1-v2. Numbers and out-of-vocabulary words are replaced with special tokens. Words, user tags and labels are all encoded as 300-dimensional vectors using \textsc{word2vec} \cite{DBLP:journals/corr/abs-1301-3781}.

@@

We compare our method with the following methods: 
\begin{itemize}
	\item \textbf{Binary Relevance (BR)} \cite{tsoumakas2007multi} with both independent training and prediction;
	\item \textbf{Binary Relevance with support inference (BR-support)} \cite{wang2017regularizing} which trains binary classifiers independently but imposes label constraints at prediction time by only considering label sets observed during training, namely $\hat{\mathbf{y}}=\arg\max_{\text{observed~}\mathbf{y}}\prod_{\ell=1}^L p(y_{\ell}|x)$;
	\item \textbf{Probabilistic Classifier Chain (PCC)} \cite{DBLP:conf/icml/DembczynskiCH10} which transforms the multi-label classification task into a chain of binary classification problems.
    \item \textbf{Sequence to Sequence RNN (seq2seq-RNN)} \cite{DBLP:conf/nips/NamMKF17} which maps each set to a sequence by decreasing label frequency and solves the multi-label task with an RNN designed for sequence prediction (see Table \ref{tab_objs}). 
    \item \textbf{Vinyals-RNN-uniform, Vinyals-RNN-sample, and Vinyals-RNN-max} are three variants of RNNs proposed by \cite{vinyals2015order}. They are trained  with different objectives that correspond to different transformations between sets and sequences. See Table~\ref{tab_objs} for a summary of their training objectives. Following the approach taken by \cite{vinyals2015order}, Vinyals-RNN-sample and Vinyals-RNN-max are initialized by Vinyals-RNN-uniform. We have also tested training Vinyals-RNN-max directly without having Vinyals-RNN-uniform as an initialization, and we name it as  \textbf{Vinyals-RNN-max-direct}.
    \item \textbf{Sequence Generation Model (SGM)} \cite{DBLP:journals/corr/abs-1806-04822} which trains the RNN model similar to seq2seq-RNN but uses a new decoder structure that computes a weighted global embedding based on all labels as opposed to just the top one at each time step.
\end{itemize}

@@

Table \ref{tab:main} shows the performance of different methods in terms of \emph{label-F1} and \emph{instance-F1}. The SGM results are taken directly from \cite{DBLP:journals/corr/abs-1806-04822}, and are originally reported only on AAPD dataset in terms of Hamming-Loss and Micro-F1. Definitions of these two metrics can be found in \cite{koyejo2015consistent}.  
% The second best method is the variant of our method without the sequence probability summation at prediction. Comparing these two, we can see the benefit of summing up sequence probabilities at prediction time (the beam search for summation step does not add much computation).

@@

\begin{figure}[t]
%\hspace{-2ex}
\includegraphics[width=1.0\columnwidth]{figs/labelf1.png}

\caption{Average F1 over rare labels with the same frequency on TheGuardian dataset. Orange=set-RNN, Red=seq2seq-RNN.}
\label{fig:labelf1}
%\vspace{-6ex}
\end{figure}

@@

Next we analyze how much benefit our new set prediction strategy brings in. For each RNN-based method, we test two prediction strategies: 1) finding the sequence with the highest probability and outputting the corresponding set (this is the default prediction strategy for all models except set-RNN); 2) outputting the set with the highest approximated probability (this is the default prediction strategy for set-RNN). Table~\ref{table_prediction} shows how each method performs with these two prediction strategies. One can see that Vinyals-RNN-uniform and set-RNN benefit most from predicting the top set,  Vinyals-RNN-sample, Vinyals-RNN-max and Vinyals-RNN-max-direct benefit less, and seq2seq RNN does not benefit at all. Intuitively, for the top-set prediction to be different from the top-sequence prediction, the model has to spread probability mass across different sequence permutations of the same set.

>>>>

We test our proposed set-RNN method on 4 real-world datasets, RCV1-v2, Slashdot, TheGuardian, and Arxiv Academic Paper Dataset (AAPD) \cite{DBLP:journals/corr/abs-1806-04822}. We take the public RCV1-v2 release\footnote{\scriptsize\url{http://www.ai.mit.edu/projects/jmlr/papers/volume5/lewis04a/lyrl2004_rcv1v2_README.htm}} and randomly sample 50,000 documents. We crawl Slashdot and TheGuardian documents from their websites\footnote{\scriptsize Slashdot: \url{https://slashdot.org/} Note that there is another public Slashdot multi-label dataset \cite{read2009classifier} but we do not use that one because it is quite small. TheGuardian: \url{https://www.theguardian.com} 
} and treat the official editor tags as ground truth. We also gather a list of user tags\footnote{\scriptsize \url{www.zubiaga.org/datasets/socialbm0311/}} for each document and treat them as additional features. For AAPD dataset, we follow the same train/test split as in \cite{DBLP:journals/corr/abs-1806-04822}. Table \ref{tab:stats} contains statistics of these four datasets. Links to document, official editor tags, and user tags are avaliable at \url{http://www.ccis.neu.edu/home/kechenqin}. 
\begin{table}[h]
	\resizebox{1.01\columnwidth}{!}{%resize the table
\begin{tabular}{|l|c|c|c|c|c|c|}
 \hline
 Data & \#Train & \#Test & Cardinality & \#Labels & Doc length \\
 \hline
 Slashdot & 19,258 & 4,814& 4.15& 291&64 \\
 RCV1-v2 & 40,000& 10,000& 3.17& 101&121 \\
 TheGuardian & 37,638 & 9,409 & 7.41& 1,527&505 \\
 AAPD & 53,840 & 1,000 & 2.41& 54 & 163 \\
 \hline
\end{tabular}
}
\caption{\fontsize{10}{12}\selectfont Statistics of the datasets.}\label{tab:stats}
\end{table}

\begin{table*}[ht]
	\begin{center}
	\resizebox{2.1\columnwidth}{!}{%resize the table
		\begin{tabular}{|l|cc|cc|cc|cccc|}
			\hline
			\multirow{2}{*}{Methods}	& 
       \multicolumn{2}{c|}{Slashdot}&\multicolumn{2}{c|}{RCV1-v2}&\multicolumn{2}{c|}{TheGuardian}&\multicolumn{4}{c|}{AAPD} \\
       \cline{2-11}
      & label-F1 & instance-F1 & label-F1 & instance-F1 & label-F1 & instance-F1 & label-F1 & instance-F1 & hamming-loss & micro-F1 \\

@@

 To process documents, we filter out stopwords and punctuations. Each document is truncated to have maximum 500 words for TheGuardian and AAPD, and 120 for Slashdot and RCV1-v2. Zero padding is used if the document contains less words than the maximum number. Numbers and out-of-vocabulary words are replaced with special tokens. Words, user tags and labels are all encoded as 300-dimensional vectors using \textsc{word2vec} \cite{DBLP:journals/corr/abs-1301-3781}.

@@

We compare our method with the following methods: 
\begin{itemize}
	\item \textbf{Binary Relevance (BR)} \cite{tsoumakas2007multi} with both independent training and prediction;
	\item \textbf{Binary Relevance with support inference (BR-support)} \cite{wang2018pipeline} which trains binary classifiers independently but imposes label constraints at prediction time by only considering label sets observed during training, namely $\hat{\mathbf{y}}=\arg\max_{\text{observed~}\mathbf{y}}\prod_{\ell=1}^L p(y_{\ell}|x)$;
	\item \textbf{Probabilistic Classifier Chain (PCC)} \cite{DBLP:conf/icml/DembczynskiCH10} which transforms the multi-label classification task into a chain of binary classification problems. Predictions are made with Beam Search.
  \item \textbf{Sequence to Sequence RNN (seq2seq-RNN)} \cite{DBLP:conf/nips/NamMKF17} which maps each set to a sequence by decreasing label frequency and solves the multi-label task with an RNN designed for sequence prediction (see Table \ref{tab_objs}). 
  \item \textbf{Vinyals-RNN-uniform, Vinyals-RNN-sample, and Vinyals-RNN-max} are three variants of RNNs proposed by \cite{vinyals2015order}. They are trained with different objectives that correspond to different transformations between sets and sequences. See Table~\ref{tab_objs} for a summary of their training objectives. Following the approach taken by \cite{vinyals2015order}, Vinyals-RNN-sample and Vinyals-RNN-max are initialized by Vinyals-RNN-uniform. We have also tested training Vinyals-RNN-max directly without having Vinyals-RNN-uniform as an initialization, and we name it as \textbf{Vinyals-RNN-max-direct}.
  \item \textbf{Sequence Generation Model (SGM)} \cite{DBLP:journals/corr/abs-1806-04822} which trains the RNN model similar to seq2seq-RNN but uses a new decoder structure that computes a weighted global embedding based on all labels as opposed to just the top one at each timestep.
\end{itemize}

@@

Table \ref{tab:main} shows the performance of different methods in terms of \emph{label-F1} and \emph{instance-F1}. The SGM results are taken directly from \cite{DBLP:journals/corr/abs-1806-04822}, and are originally reported only on AAPD dataset in terms of \emph{hamming-loss} and \emph{micro-F1}. Definitions of these two metrics can be found in \cite{koyejo2015consistent}. 
% The second best method is the variant of our method without the sequence probability summation at prediction. Comparing these two, we can see the benefit of summing up sequence probabilities at prediction time (the beam search for summation step does not add much computation).

@@

\begin{figure}[t]
%\hspace{-2ex}
\includegraphics[width=1.0\columnwidth]{figs/labelf1_v2.png}

\caption{Average F1 over rare labels with the same frequency on TheGuardian dataset. Blue($\Delta$)=set-RNN, Red($\cdot$)=seq2seq-RNN.}
\label{fig:labelf1}
%\vspace{-6ex}
\end{figure}

@@

Next we analyze how much benefit our new set prediction strategy brings in. For each RNN-based method, we test two prediction strategies: 1) finding the sequence with the highest probability and outputting the corresponding set (this is the default prediction strategy for all models except set-RNN); 2) outputting the set with the highest probability (this is the default prediction strategy for set-RNN). Table~\ref{table_prediction} shows how each method performs with these two prediction strategies. One can see that Vinyals-RNN-uniform and set-RNN benefit most from predicting the top set, Vinyals-RNN-sample, Vinyals-RNN-max and Vinyals-RNN-max-direct benefit less, and seq2seq RNN does not benefit at all. Intuitively, for the top-set prediction to be different from the top-sequence prediction, the model has to spread probability mass across different sequence permutations of the same set.
